Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/proof-reconstruction/resolve.tex
[ paper ] fixed typos in resolve.

From now, we assume all propositions to be right-associative unless
otherwise stated.

The $\ffactor$ function in~\eqref{eq:factor-definition}
simplifies a special case of disjunction, the repeated disjuncts
(\eg, $\ffactor~(φ ∨ φ)~=~φ$).
Notice that other cases like $φ~∨~(ψ~∨~φ)$ do no reduce to $ψ~∨~φ$.

@@

\begin{myremark}
Notice that using $\fsbuild_{∨}$ we can build not only a disjunction
with the same disjuncts of the source formula but also a complete different
disjunction by adding new disjuncts to the source formula.
\end{myremark}

The following lemma tries to reorder nested disjunctions
by forcing the formula to be in right-associative form in order to
apply Lemma~\ref{lem:sbuild-or}.

@@

Now, we define function to work with nested conjunctions. This will
help us in the end of this section to reorder conjunctive normal forms.
For instance, the $\freorder_{∧}$ function in~\eqref{eq:reorder-and},
reorders nested conjunctions.

>>>>

From now on, we assume all propositions to be right-associative unless
otherwise stated.

The $\ffactor$ function in~\eqref{eq:factor-definition}
simplifies a special case of disjunction, the repeated disjuncts
(\eg, $\ffactor~(φ ∨ φ)~=~φ$).
Notice that other cases like $φ~∨~(ψ~∨~φ)$ do no reduce to $ψ~∨~φ$.
We use this function in Lemma~\ref{lem:sbuild-or}.

@@

\begin{myremark}
Notice that using $\fsbuild_{∨}$ we can build not only a disjunction
with the same disjuncts of the source formula but also a complete different
disjunction by adding new disjuncts to the source formula
via introduction rules for disjunctions.
\end{myremark}

The following lemma aims to reorder nested disjunctions
by forcing the formula to be in right-associative form in order to
apply Lemma~\ref{lem:sbuild-or}.

@@

Now, we define the $\freorder_{∧}$ function in~\eqref{eq:reorder-and} to
reorder nested conjunctions. This will help us in the end of this section to
reorder conjunctive normal forms. For instance,
